Equalizer Programming Guide

### 2008-07-03 Developer/ProgrammingGuide/paper.tex
Update statistics overlay documentation in Programming Guide
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.3.3 for Equalizer 0.5.1+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    1.3.1   & May 02, 2008 & Add statistics, improved images based on 1.2 print\\
    1.3.2   & May 05, 2008 & Add network distribution on eqPly model data\\
    1.3.3   & May 10-19, 2008 & File Format Appendix\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

In debug builds, a statistics overlay using the gathered statistics
events is rendered directly before \textsf{Window::swapBuffers}. The
overlay rendering method, \textsf{Channel::drawStatistics}, can be
called directly to render the overlay. It can also be overwritten by a
custom implementation.

@@

In order to facilitate the understanding, subsequent frames alternate in
brightness. The right-most, current frame is brighter than the
frame-before-last.

@@

The beginning of a frame is marked by a vertical green line, and the end
of a frame by a vertical gray line. These lines also alternate in
brightness. The brightness and color matches the event for
\textsf{Config::startFrame} and \textsf{Config::finishFrame},
respectively. The event for \textsf{startFrame} is typically not
visible, since it takes less than one millisecond to execute. If no idle
processing is done by the application, the event for
\textsf{finishFrame} occupies a full frame, since the config is blocked
here waiting for the frame to complete.

@@

>>>>

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.3.4 for Equalizer 0.5.2+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    1.3.1   & May 02, 2008 & Add statistics, improved images based on 1.2 print\\
    1.3.2   & May 05, 2008 & Add network distribution on eqPly model data\\
    1.3.3   & May 10-19, 2008 & File Format Appendix\\
    1.3.4   & July 3, 2008 & Update statistics section\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

The Equalizer examples render a statistics overlay using the gathered
statistics events directly before
\textsf{Window::swapBuffers}. Statistics are toggled on and off using
the 's' key. The overlay rendering method,
\textsf{Channel::drawStatistics}, can be called directly by any
application to render the overlay. It can also be overwritten by a
custom implementation.

@@

In order to facilitate the understanding, older frames are gradually
greyed out. The right-most, current frame is brighter than the
frame-before-last.

@@

The beginning of a frame is marked by a vertical green line, and the end
of a frame by a vertical gray line. These lines are also attenuated. The
brightness and color matches the event for \textsf{Config::startFrame}
and \textsf{Config::finishFrame}, respectively. The event for
\textsf{startFrame} is typically not visible, since it takes less than
one millisecond to execute. If no idle processing is done by the
application, the event for \textsf{finishFrame} occupies a full frame,
since the config is blocked here waiting for the frame to complete.

@@

The configuration used in this examples does not use a swap
barrier. Swap barrier tasks are solid red events directly in front of
the white swap buffer task.
